Replication on multicore considering hierarchy and characteristics of the network

### 2013-03-20 paper.tex
Machine model section

The selection of distributed algorithms depends on the characteristics
of a network. Multicores networks are heterogeneous combinations of
complex networks. %
Their diversity makes manual selection tedious. Hence, we aim for an
automatic approach for selecting algorithms for a specific
network. %
We express the network characteristics in a multicore network
model. This model is currently by no means complete. We are going to
extend it over time to address more complexities of current and future
multicores.

>>>>

Characteristics of the network influence the performance of
distributed algorithms. Multicores networks are heterogeneous
combinations of complex networks, which makes algorithm selection
hard. %
Furthermore, their diversity makes manual selection tedious. Hence, we
aim for an automatic approach for selecting algorithms for a specific
network. %
We express the network characteristics in a multicore network
model. This model at this stage is by no means complete. We are going to
extend it over time to address more complexities of current and future
multicores.
